Model

### 2019-05-29 stats/model.Rmd
add second model run

#saveRDS(sem_know_model, "../saves/sem_know_model.rds")
sem_know_model <- readRDS("../saves/sem_know_model.rds")
```

>>>>

#saveRDS(sem_know_model, "../saves/sem_know_model.rds")

# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
sem_know_model <- readRDS("../saves/sem_know_model.rds")
# 8 chains, 4000 iterations per chain, 2000 burn in, lag = 1
sem_know_model <- readRDS("../saves/sem_know_model_2.rds")
```
